% navimind_ieee.tex — IEEE 8-page double-column paper
% Compile: xelatex navimind_ieee.tex (or pdflatex if no CJK needed)
\documentclass[conference]{IEEEtran}

% ── Packages ──
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{balance}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,fit,backgrounds,calc,shapes.geometric}

% ── TBD placeholder command ──
\newcommand{\TBD}[1]{\textcolor{red}{\textbf{[TBD: #1]}}}

% ── Math shortcuts ──
\newcommand{\vp}{\mathbf{p}}
\newcommand{\vf}{\mathbf{f}}
\newcommand{\vmu}{\boldsymbol{\mu}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\Entropy}{H}

\begin{document}

% ══════════════════════════════════════════════════════════════════════
% Title & Authors
% ══════════════════════════════════════════════════════════════════════
\title{NaviMind: Belief-Aware Hierarchical Scene Graphs for\\Robust Zero-Shot Object Navigation on Quadruped Robots}

\author{
\IEEEauthorblockN{Hongsen Pang and Hanzhuo Zhang}
\IEEEauthorblockA{Shanghai Inovxio Technology Co., Ltd.\\
Shanghai, China\\
\{hongsen.pang, hanzhuo.zhang\}@inovxio.com}
}

\maketitle

% ══════════════════════════════════════════════════════════════════════
% Abstract
% ══════════════════════════════════════════════════════════════════════
\begin{abstract}
We present \textbf{NaviMind}, a zero-shot object navigation system that enables quadruped robots to navigate to targets specified by natural language in unknown environments.
NaviMind constructs a \emph{Belief-Aware Hierarchical Scene Graph} (BA-HSG) online and incrementally, organizing detected objects into a four-level hierarchy (Object--Group--Room--Floor) where each node maintains a probabilistic belief state (Beta-distributed existence prior, Gaussian position uncertainty, composite credibility).
We make three key contributions:
(1)~BA-HSG with FOV-aware belief updates and graph diffusion for principled false-positive rejection;
(2)~a Fast--Slow dual-path architecture where 75\%+ of queries are resolved via sub-millisecond multi-source fusion while complex queries use hierarchical Chain-of-Thought LLM reasoning with 90\% token reduction;
and (3)~a Value-of-Information (VoI) scheduler that replaces heuristic fixed-interval triggers with Shannon-entropy-driven information gain optimization under edge-compute budget constraints.
The system runs entirely onboard a Unitree Go2 quadruped with Jetson Orin NX (16\,GB), addressing low-viewpoint ($\sim$30\,cm), visual jitter, and terrain-constrained navigation challenges.
Ablation studies confirm that BA-HSG improves false-positive rejection over deterministic baselines, the Fast Path achieves 81.8\% hit rate at 0.28\,ms latency (92.5\% LLM token reduction via ESCA), and VoI scheduling reduces unnecessary re-perception compared to fixed-interval triggering.
\end{abstract}

\begin{IEEEkeywords}
Object Navigation, Belief Scene Graph, Uncertainty-Aware Planning, Vision-Language Navigation, Quadruped Robot, Zero-Shot
\end{IEEEkeywords}

% ══════════════════════════════════════════════════════════════════════
% I. Introduction
% ══════════════════════════════════════════════════════════════════════
\section{Introduction}
\label{sec:intro}

Object-goal navigation---the task of navigating to a target object specified by its semantic category or natural language description---is a fundamental capability for mobile robots operating in human environments~\cite{batra2020objectnav, yadav2022hm3d}.
Recent advances in large language models (LLMs) and vision-language models (VLMs) have opened new possibilities for zero-shot approaches that require no task-specific training~\cite{sgnav2024, esc2023, l3mvn2023}.
However, deploying these capabilities on real robots, particularly quadruped platforms in unknown environments, remains a significant open challenge.

\subsection{Motivation}

Current approaches face fundamental limitations when applied to real-world quadruped deployment:

\textbf{Offline map dependency.}
Methods like FSR-VLN~\cite{fsrvln2025} achieve 92\% success rate by constructing hierarchical scene graphs through offline scanning, making them inapplicable to unknown environments.
ConceptGraphs~\cite{conceptgraphs2024} and HOV-SG~\cite{hovsg2024} similarly assume pre-scanned environments.

\textbf{Flat scene representation.}
Systems like LOVON~\cite{lovon2025} and CoW~\cite{cow2023} use flat object-level matching without structured spatial reasoning.
When instructions involve spatial relations (``the fire extinguisher near the door'') or room-level context (``go to the office''), flat representations fail to provide hierarchical context for disambiguation.

\textbf{No dynamic adaptation.}
Most systems assume static environments~\cite{fsrvln2025, hovsg2024}.
Without mechanisms to verify and update target beliefs during navigation, false-positive detections lead to irreversible failures.

\textbf{Quadruped-specific challenges.}
Quadruped robots introduce extremely low camera viewpoint ($\sim$30\,cm vs.\ $\sim$90\,cm for wheeled robots), significant visual jitter from walking gaits, and limited field of view.
Only LOVON~\cite{lovon2025} and NaVILA~\cite{navila2025} address quadruped navigation, but neither uses structured scene graphs.

\subsection{Contributions}

We make the following contributions:

\begin{enumerate}[leftmargin=*]
\item \textbf{Belief-Aware Hierarchical Scene Graph (BA-HSG).}
A four-level scene graph (Object--Group--Room--Floor) where each node maintains a Beta-distributed existence belief, Gaussian position uncertainty, and composite credibility.
FOV-aware negative evidence and graph diffusion enable principled false-positive rejection.

\item \textbf{Adaptive Fast--Slow Dual-Path Inference.}
Multi-source confidence fusion resolves 81.8\% of queries in $<$1\,ms without LLM calls (0.28\,ms on 200-object scenes).
Complex queries trigger selective grounding (92.5\% token reduction via ESCA) and hierarchical Chain-of-Thought LLM reasoning.
An AdaNav entropy trigger forces slow-path escalation when candidate score entropy exceeds a threshold.

\item \textbf{VoI-Driven Reasoning Scheduling.}
The decision of when to re-perceive, invoke slow reasoning, or continue navigation is formalized as Shannon-entropy-based information gain optimization under edge-compute constraints, replacing heuristic fixed-interval triggers.
\end{enumerate}

The system is validated on a Unitree Go2 quadruped with Jetson Orin NX (16\,GB), with ablation studies quantifying each contribution.

% ══════════════════════════════════════════════════════════════════════
% II. Related Work
% ══════════════════════════════════════════════════════════════════════
\section{Related Work}
\label{sec:related}

\subsection{Scene Graph Navigation}

3D scene graphs provide structured representations encoding objects, attributes, and inter-object relationships.
Hydra~\cite{hydra2022} constructs 5-level real-time scene graphs using metric-semantic meshes.
ConceptGraphs~\cite{conceptgraphs2024} builds open-vocabulary 3D scene graphs incrementally from RGB-D, leveraging CLIP~\cite{clip2021} for semantic encoding.
HOV-SG~\cite{hovsg2024} extends this to multi-floor hierarchical graphs.

Most relevant to our work, SG-Nav~\cite{sgnav2024} constructs online hierarchical scene graphs with LLM-based Chain-of-Thought prompting, achieving state-of-the-art zero-shot performance on MP3D and HM3D ($>$10\% SR improvement).
FSR-VLN~\cite{fsrvln2025} proposes a four-level HMSG with Fast-to-Slow reasoning on a humanoid, but requires offline scanning.
DovSG~\cite{dovsg2024} addresses dynamic environments with local update mechanisms but lacks formal uncertainty modeling.

NaviMind extends SG-Nav's paradigm with three innovations: (i)~belief-aware nodes with calibrated uncertainty, (ii)~VoI-driven scheduling, and (iii)~risk-sensitive multi-hypothesis planning.

\subsection{Zero-Shot Object-Goal Navigation}

Zero-shot methods eliminate task-specific training by leveraging pre-trained foundation models.
CoW~\cite{cow2023} uses CLIP matching for zero-shot navigation.
ESC~\cite{esc2023} uses LLM captioning to guide frontier exploration.
L3MVN~\cite{l3mvn2023} prompts LLMs with object lists for frontier selection.
VLFM~\cite{vlfm2024} generates language-grounded value maps from RGB observations, achieving SOTA SPL on Boston Dynamics Spot.

Unlike flat-representation methods, NaviMind uses hierarchical scene graphs for structured context and avoids LLM calls for 81.8\% of queries via the Fast Path.

\subsection{Dual-Process Reasoning and Uncertainty}

Inner Monologue~\cite{innermonologue2023} grounds LLM planning with environment feedback.
SayCan~\cite{saycan2022} combines LLM knowledge with robotic affordances.
LERa~\cite{lera2025} introduces Learn-Execute-Replan with experience accumulation.

SG-Nav~\cite{sgnav2024} proposes graph-based re-perception with scalar credibility, but without formal uncertainty modeling.
Classical active perception uses information-theoretic criteria (entropy reduction, mutual information) for sensing action selection~\cite{howard1966voi}.
Our VoI scheduler adopts this principle, formalizing re-perception and slow-reasoning triggers as entropy-driven information gain optimization.

\subsection{Quadruped Navigation}

LOVON~\cite{lovon2025} integrates LLM planning with open-vocabulary detection on Unitree quadrupeds, using Laplacian blur filtering.
NaVILA~\cite{navila2025} proposes an end-to-end VLA model trained on human videos.
OrionNav~\cite{orionnav2024} constructs semantic scene graphs with LLM planning on quadrupeds but lacks hierarchical CoT and re-perception.
VLN-PE~\cite{vlnpe2025} reveals that quadrupeds suffer from restricted observation space and locomotion-induced visual degradation.

NaviMind is the first system combining online hierarchical scene graph construction, belief-aware updates, dual-path reasoning, and VoI scheduling on a quadruped platform.
Table~\ref{tab:comparison} summarizes the comparison.

\begin{table}[t]
\centering
\caption{Comparison with related systems.}
\label{tab:comparison}
\footnotesize
\setlength{\tabcolsep}{2pt}
\begin{tabular}{@{}lccccccc@{}}
\toprule
System & SG & Hier. & Online & Belief & Explore & Quad. & ZS \\
\midrule
SG-Nav~\cite{sgnav2024}        & \checkmark & 3-lvl & \checkmark & -- & LLM  & -- & \checkmark \\
FSR-VLN~\cite{fsrvln2025}      & \checkmark & 4-lvl & --         & -- & --   & -- & \checkmark \\
LOVON~\cite{lovon2025}          & --         & --    & --         & -- & --   & \checkmark & \checkmark \\
OrionNav~\cite{orionnav2024}    & \checkmark & flat  & \checkmark & -- & LLM  & \checkmark & \checkmark \\
VLFM~\cite{vlfm2024}            & --         & --    & --         & -- & VLM  & -- & \checkmark \\
DovSG~\cite{dovsg2024}          & \checkmark & flat  & \checkmark & -- & --   & -- & \checkmark \\
\textbf{NaviMind}                & \checkmark & 4-lvl & \checkmark & \checkmark & TSG+LLM & \checkmark & \checkmark \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

% ══════════════════════════════════════════════════════════════════════
% III. Method
% ══════════════════════════════════════════════════════════════════════
\section{Method}
\label{sec:method}

NaviMind consists of three modules (Fig.~\ref{fig:architecture}):
a \emph{Perception Module} (\S\ref{sec:bahsg}) that constructs and maintains an online BA-HSG $\mathcal{G}$;
a \emph{Planning Module} (\S\ref{sec:fastslow}) that resolves natural language instructions via Fast--Slow dual-path reasoning;
and an \emph{Exploration Module} that selects frontiers when the target is absent from $\mathcal{G}$.
All modules run onboard Jetson Orin NX with no cloud dependency except optional LLM API calls.

\begin{figure*}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
    >=Stealth,
    node distance=0.6cm and 0.8cm,
    every node/.style={font=\small},
    layer/.style={draw, rounded corners=3pt, minimum height=0.7cm, text centered, font=\small\sffamily},
    hw/.style={layer, fill=gray!15, minimum width=2.4cm},
    sense/.style={layer, fill=blue!12, minimum width=2.4cm},
    slam/.style={layer, fill=cyan!12, minimum width=2.4cm},
    perc/.style={layer, fill=green!12, minimum width=2.8cm},
    plan/.style={layer, fill=orange!12, minimum width=2.8cm},
    orch/.style={layer, fill=red!10, minimum width=2.4cm},
    inter/.style={layer, fill=purple!10, minimum width=2.4cm},
    ring/.style={draw, dashed, rounded corners=4pt, fill=yellow!8, minimum height=0.6cm, font=\small\sffamily},
    arr/.style={->, thick, color=black!70},
    darr/.style={<->, thick, color=black!50, dashed},
]

% ── L1 Drivers ──
\node[hw] (lidar) {Livox Mid-360};
\node[hw, right=0.6cm of lidar] (rgbd) {Orbbec RGB-D};
\node[hw, right=0.6cm of rgbd] (imu) {IMU};
\node[hw, right=0.6cm of imu] (dog) {Quadruped};

% ── L2 SLAM ──
\node[slam, above=0.7cm of $(lidar)!0.5!(imu)$] (fastlio) {Fast-LIO2 / Point-LIO};

% ── L3 Perception ──
\node[perc, above=0.7cm of rgbd] (yolo) {YOLO11s-seg (BPU)};
\node[perc, right=0.5cm of yolo] (clip) {MobileCLIP};
\node[perc, above=0.7cm of $(yolo)!0.5!(clip)$] (bahsg) {\textbf{BA-HSG} $\mathcal{G}$};
\node[sense, left=0.3cm of yolo] (terrain) {Terrain Analysis};

% ── L4 Planning ──
\node[plan, above=0.9cm of bahsg] (fastslow) {\textbf{Fast--Slow} Goal Resolution};
\node[plan, left=1.2cm of fastslow] (frontier) {Frontier Scorer};
\node[plan, right=1.2cm of fastslow] (voi) {\textbf{VoI} Scheduler};

% ── L5 Orchestration ──
\node[orch, above=0.7cm of fastslow] (mission) {Mission Arc FSM};
\node[orch, left=0.8cm of mission] (global) {PCT Global Planner};
\node[orch, right=0.8cm of mission] (local) {Local Planner};

% ── L6 Interaction ──
\node[inter, above=0.7cm of mission] (grpc) {gRPC Gateway :50051};
\node[inter, right=0.8cm of grpc] (flutter) {Flutter App};

% ── Three Rings (orthogonal) ──
\node[ring, right=2.0cm of dog] (r1) {R1 Safety};
\node[ring, above=0.3cm of r1] (r2) {R2 Eval};
\node[ring, above=0.3cm of r2] (r3) {R3 Dialogue};

% ── Arrows: L1 → L2/L3 ──
\draw[arr] (lidar) -- (fastlio);
\draw[arr] (imu) -- (fastlio);
\draw[arr] (rgbd) -- (yolo);

% ── L2 → L3 ──
\draw[arr] (fastlio) -| node[pos=0.3, above, font=\scriptsize]{odom + map} (terrain);
\draw[arr] (fastlio) -- (bahsg);

% ── L3 internal ──
\draw[arr] (yolo) -- (bahsg);
\draw[arr] (clip) -- (bahsg);
\draw[arr] (terrain) |- (local);

% ── L3 → L4 ──
\draw[arr] (bahsg) -- node[right, font=\scriptsize]{scene graph} (fastslow);
\draw[arr] (bahsg) -| (frontier);

% ── L4 internal ──
\draw[darr] (fastslow) -- (voi);
\draw[arr] (frontier) -- (fastslow);

% ── L4 → L5 ──
\draw[arr] (fastslow) -- node[right, font=\scriptsize]{goal} (mission);
\draw[arr] (mission) -- (global);
\draw[arr] (mission) -- (local);
\draw[arr] (global) -- node[above, font=\scriptsize]{path} (local);

% ── L5 → L6 ──
\draw[arr] (mission) -- (grpc);
\draw[darr] (grpc) -- (flutter);

% ── L5 → L1 (cmd_vel) ──
\draw[arr] (local) -- node[right, font=\scriptsize]{cmd\_vel} (dog);

% ── VoI feedback loop ──
\draw[arr, color=red!60, densely dashed] (voi) to[out=-20, in=20] node[right, font=\scriptsize, color=red!70]{re-perceive} (bahsg);

% ── Ring connections ──
\draw[arr, color=gray, thin, dotted] (r1) -- (dog);

% ── NL instruction input ──
\node[above=0.15cm of grpc, font=\scriptsize\itshape, color=black!60] {NL instruction};

\end{tikzpicture}%
}
\caption{NaviMind system architecture. The perception module (L3) constructs a BA-HSG online from RGB-D detections (YOLO11s-seg on BPU), MobileCLIP features, and LiDAR-inertial odometry (L2). The planning module (L4) resolves natural language goals via Fast--Slow dual-path reasoning. The VoI scheduler triggers adaptive re-perception (dashed red arrow) when belief entropy is high. Three orthogonal rings (R1--R3) provide safety, evaluation, and dialogue feedback.}
\label{fig:architecture}
\end{figure*}

\subsection{BA-HSG Construction and FOV-Aware Update}
\label{sec:bahsg}

\subsubsection{Scene Graph Definition}

We define the hierarchical scene graph as $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with four node levels:
\begin{equation}
\mathcal{V} = \mathcal{V}^{\text{obj}} \cup \mathcal{V}^{\text{grp}} \cup \mathcal{V}^{\text{room}} \cup \mathcal{V}^{\text{floor}}
\end{equation}

\noindent\textbf{Object nodes} $v_i^{\text{obj}} = (\ell_i, \vp_i, \vf_i, s_i, n_i)$ store a semantic label $\ell_i$, 3D position $\vp_i \in \mathbb{R}^3$, CLIP feature $\vf_i \in \mathbb{R}^{512}$, best detection score $s_i$, and detection count $n_i$.
\textbf{Room nodes} aggregate semantically coherent spatial regions with inferred names (e.g., ``corridor'', ``office'').
\textbf{Group nodes} cluster related objects within rooms.
Edges include hierarchical affiliation (Object$\leftrightarrow$Group$\leftrightarrow$Room$\leftrightarrow$Floor) and spatial relations (near, on, left\_of, etc.).

\subsubsection{Node-Level Belief State}

Each object $v_i$ is augmented with three belief components:

\textbf{Existence belief} via Beta distribution:
\begin{equation}
P(\text{exists}_i) \sim \text{Beta}(\alpha_i, \beta_i), \quad \bar{P}_i = \frac{\alpha_i}{\alpha_i + \beta_i}
\label{eq:existence}
\end{equation}
Positive evidence (high-confidence detection with valid depth and geometric consistency) and negative evidence (object within camera FOV but undetected) update the parameters as:
\begin{equation}
\alpha_i' = \alpha_i + \mathbb{1}[\text{hit}], \quad
\beta_i' = \beta_i + \eta_{\text{neg}} \cdot \mathbb{1}[\text{miss}]
\label{eq:belief_update}
\end{equation}
where $\eta_{\text{neg}} = 0.5$ down-weights negative evidence to account for detection noise.
A miss is only counted when the object falls within the camera frustum (see below).

\textbf{Position uncertainty} via isotropic Gaussian:
\begin{equation}
\vp_i \sim \mathcal{N}(\vmu_i, \sigma_i^2 \mathbf{I})
\end{equation}
Updated via Kalman-style fusion with depth-proportional observation noise $\sigma_{\text{obs}} = \sigma_0 + \sigma_d \cdot d$.

\textbf{Composite credibility}:
\begin{equation}
C_i = w_s \bar{P}_i + w_v A_i + w_t e^{-\Delta t_i / \tau_t} + w_g e^{-\epsilon_i^{\text{reproj}} / \kappa}
\label{eq:credibility}
\end{equation}
where $A_i = 1 - 1/n_i$ captures view diversity, $\Delta t_i$ is staleness, and $\epsilon_i^{\text{reproj}}$ is reprojection error.

\subsubsection{FOV-Aware Negative Evidence}

Unlike prior work that applies negative evidence globally~\cite{sgnav2024}, we restrict miss counting to objects within the camera's frustum.
An object $v_i$ at position $\vp_i$ is within the FOV of a camera at position $\vp_{\text{cam}}$ with forward direction $\vf_{\text{cam}}$ iff:
\begin{equation}
\cos\!\left(\angle(\vp_i - \vp_{\text{cam}},\; \vf_{\text{cam}})\right) > \cos\!\frac{\theta}{2}
\;\;\wedge\;\;
\|\vp_i - \vp_{\text{cam}}\| < d_{\max}
\label{eq:fov}
\end{equation}
where $\theta$ is the horizontal field of view and $d_{\max}$ is the maximum reliable depth.
Only objects satisfying Eq.~\eqref{eq:fov} but undetected receive negative evidence updates via Eq.~\eqref{eq:belief_update}.
This prevents penalizing objects that are simply out of view, significantly reducing false negatives in the belief update.

\subsubsection{Graph Diffusion}

Credibility propagates through the hierarchy.
\textbf{Upward}---room credibility is the detection-weighted average of its objects':
$C_k^{\text{room}} = \sum_{i \in \mathcal{O}_k} n_i C_i \big/ \sum_{i \in \mathcal{O}_k} n_i$.
\textbf{Downward}---well-established rooms boost newly detected child objects via:
\begin{equation}
\bar{P}'(\text{child}) = \bar{P}(\text{child}) + w_{\downarrow}\!\left(C_k^{\text{room}} - C_{\text{prior}}^{\text{room}}\right)
\label{eq:diffusion}
\end{equation}
where $w_{\downarrow}$ controls the diffusion strength and $C_{\text{prior}}^{\text{room}}$ is the room's prior credibility before the current update.
This allows newly detected objects in a well-characterized room (e.g., ``office'' with many confirmed objects) to receive a credibility boost, accelerating convergence.
\textbf{Lateral}---spatially related objects share partial credibility evidence.

\subsection{Adaptive Fast--Slow Goal Resolution}
\label{sec:fastslow}

\subsubsection{Fast Path: Multi-Source Confidence Fusion}

The Fast Path computes a fused confidence score for each object without LLM calls:
\begin{equation}
s_{\text{fused}}(v_i, I) = \sum_{k} w_k \cdot s_k = w_\ell s_{\text{label}} + w_c s_{\text{clip}} + w_d s_{\text{det}} + w_r s_{\text{spatial}}
\label{eq:fusion}
\end{equation}
where $s_{\text{label}}$ uses keyword extraction (supporting Chinese via jieba), $s_{\text{clip}}$ is CLIP cosine similarity, $s_{\text{det}}$ is YOLO-World confidence, and $s_{\text{spatial}}$ captures spatial relation hints.
Weights are $w_\ell = w_c = 0.35$, $w_d = w_r = 0.15$.

If $\max_i s_{\text{fused}} \geq \tau_{\text{fast}} = 0.75$, the Fast Path returns the result directly.
Otherwise, the system escalates to the Slow Path.

\textbf{AdaNav entropy trigger.}
After scoring, we compute the Shannon entropy over candidate scores:
\begin{equation}
\Entropy_{\text{score}} = -\sum_i \hat{p}_i \log_2 \hat{p}_i, \quad \hat{p}_i = \frac{s_i}{\sum_j s_j}
\label{eq:adanav}
\end{equation}
If $\Entropy_{\text{score}} > 1.5$ and confidence $< 0.85$, the system forces escalation to the Slow Path regardless of the maximum score, following the AdaNav uncertain-action-rejection principle.

\subsubsection{Slow Path: Hierarchical CoT LLM Reasoning}

For complex queries, the Slow Path invokes an LLM with selective grounding:
(1)~Semantic ranking filters objects by CLIP + keyword relevance;
(2)~1-hop relation expansion preserves spatial context;
(3)~capacity limits retain top-$K{=}15$ objects and top-$M{=}20$ relations, achieving $\sim$90\% token reduction.

The ESCA filtering ratio quantifies the token reduction achieved:
\begin{equation}
R_{\text{ESCA}} = 1 - \frac{|\mathcal{V}_{\text{filtered}}| + |\mathcal{E}_{\text{filtered}}|}{|\mathcal{V}| + |\mathcal{E}|}
\label{eq:esca}
\end{equation}
where $\mathcal{V}_{\text{filtered}}$, $\mathcal{E}_{\text{filtered}}$ are the nodes and edges retained after selective grounding.
In practice, $R_{\text{ESCA}} \approx 0.90$ (200 objects $\to$ $\sim$15 objects), drastically reducing LLM prompt length and cost.

The LLM receives a structured hierarchical prompt (Room$\to$Group$\to$Object) and returns target coordinates with a 4-step reasoning chain.

\subsection{VoI-Driven Reasoning Scheduling}
\label{sec:voi}

Instead of fixed-interval re-perception (every 2\,m), we formalize scheduling as Value of Information optimization over three meta-actions: \textsc{continue}, \textsc{reperceive}, and \textsc{slow\_reason}.

\subsubsection{Information Gain via Shannon Entropy}

We model the target belief as $\text{Beta}(\alpha, \beta)$ with mean $p = \alpha/(\alpha+\beta)$.
The current uncertainty is measured by binary Shannon entropy:
\begin{equation}
\Entropy(p) = -p \log_2 p - (1{-}p) \log_2(1{-}p)
\label{eq:entropy}
\end{equation}

For each action $a$ with equivalent observation strength $n_a$, we estimate the expected information gain as the reduction in Shannon entropy:
\begin{equation}
\Delta I(a) = \Entropy_{\text{before}} - \mathbb{E}\!\left[\Entropy_{\text{after}} \mid a\right]
\label{eq:infogain}
\end{equation}
where $\Entropy_{\text{before}} = \Entropy(p)$ from Eq.~\eqref{eq:entropy} and the expected posterior entropy is computed by marginalizing over positive and negative observation outcomes under the current Beta prior:
\begin{equation}
\mathbb{E}[\Entropy_{\text{after}}] = p \cdot \Entropy\!\left(\frac{\alpha + n_a}{\alpha + \beta + n_a}\right) + (1{-}p) \cdot \Entropy\!\left(\frac{\alpha}{\alpha + \beta + n_a}\right)
\end{equation}
The Beta distribution variance $\Var[\text{Beta}(\alpha,\beta)] = \alpha\beta / [(\alpha{+}\beta)^2(\alpha{+}\beta{+}1)]$ decreases with total observations $\alpha{+}\beta$, so weaker priors yield larger $\Delta I$ per observation---a natural consequence of Bayesian updating.

\subsubsection{Utility Function}

Each action's utility combines information gain and execution cost:
\begin{equation}
U(a) = k \cdot \Delta I(a) - \lambda_t T(a) - \lambda_e E(a) - \lambda_d d(a)
\label{eq:utility}
\end{equation}
where $T(a)$, $E(a)$, $d(a)$ are time, energy, and distance costs respectively.
Observation strengths are $n_{\text{continue}}{=}0.2$, $n_{\text{reperceive}}{=}2.0$, $n_{\text{slow}}{=}5.0$.

\subsubsection{Safety Rules and Cooldown}

Hard constraints override VoI optimization:
(i)~credibility below $\tau_{\text{danger}}{=}0.3$ forces immediate re-perception;
(ii)~credibility above $\tau_{\text{safe}}{=}0.7$ with proximity $<$3\,m forces continue;
(iii)~cooldown timers prevent oscillation ($T_{\text{cool}}^{\text{rep}}{=}5$\,s, $T_{\text{cool}}^{\text{slow}}{=}15$\,s);
(iv)~diminishing returns scale slow-reasoning gain by $1/(1+0.3 n_{\text{slow\_count}})$.

\subsection{Edge Deployment}
\label{sec:edge}

\subsubsection{BPU Acceleration}

On the Horizon RDK platform (128 TOPS BPU), we deploy YOLO11s-seg for instance segmentation at $\sim$45\,ms/frame.
The BPU processes NV12 input via \texttt{HB\_HBMRuntime} API, with batched prototype-coefficient matrix multiplication for mask decoding.

\subsubsection{Safety Architecture}

A three-ring cognitive architecture ensures operational safety:
Ring~1 (reflex) aggregates sensor health and emergency stops;
Ring~2 (cognition) evaluates cross-track error and progress rate;
Ring~3 (dialogue) provides unified user state feedback.

% ══════════════════════════════════════════════════════════════════════
% IV. Experiments
% ══════════════════════════════════════════════════════════════════════
\section{Experiments}
\label{sec:experiments}

\subsection{Experimental Setup}

\subsubsection{Platform}

We deploy NaviMind on a Unitree Go2 quadruped equipped with:
Horizon RDK S100P (128 TOPS BPU);
Orbbec Gemini 335 RGB-D camera (640$\times$480 @ 30\,fps);
Livox Mid-360 LiDAR;
Fast-LIO2 for SLAM.
Camera height is $\sim$30\,cm, mounted on the robot body.

\subsubsection{Benchmarks}

We evaluate NaviMind on two complementary benchmarks:

\textbf{(1) HM3D ObjectNav}~\cite{yadav2022hm3d}: The standard Habitat benchmark with 2,000 validation episodes across 6 object categories (chair, couch, bed, toilet, potted plant, TV) in 20 photorealistic indoor scenes.
We use ground-truth semantic sensor following prior zero-shot work~\cite{sgnav2024, vlfm2024} with discrete action space (forward 0.25\,m, turn $\pm$30\textdegree, stop).
Success distance is 1.0\,m.

\textbf{(2) Real-robot benchmark}: A three-level benchmark with 45 bilingual (Chinese/English) instructions on our Unitree Go2 platform:
L1 (Simple, 20): single target, direct reference;
L2 (Spatial, 15): spatial relations or room context;
L3 (Multi-step, 10): sequential or conditional instructions.

\subsubsection{Metrics}

\textbf{Primary}: Success Rate (SR), Success weighted by Path Length (SPL)~\cite{batra2020objectnav, anderson2018eval}, and SoftSPL (progress-weighted efficiency).
\textbf{Algorithmic}: Fast Path hit rate, latency, ESCA token reduction rate.

\subsection{Main Results: HM3D ObjectNav}

\begin{table}[t]
\centering
\caption{Comparison with zero-shot methods on HM3D ObjectNav.
$\dagger$~results from original papers on val (2,000 episodes).
$\ddagger$~NaviMind evaluated on val\_mini (30 episodes, 2 scenes);
direct numerical comparison is indicative due to scale difference.}
\label{tab:hm3d_main}
\footnotesize
\begin{tabular}{@{}lcccc@{}}
\toprule
Method & SR (\%) & SPL (\%) & SoftSPL (\%) & DTG (m) \\
\midrule
\multicolumn{5}{@{}l}{\textit{2023–2024 zero-shot methods (val, 2K eps)}} \\
CoW~\cite{cow2023}$^\dagger$            & 26.7 & 10.5 & -- & -- \\
ESC~\cite{esc2023}$^\dagger$            & 38.0 & 17.0 & -- & -- \\
VLFM~\cite{vlfm2024}$^\dagger$          & 38.5 & 16.6 & -- & -- \\
L3MVN~\cite{l3mvn2023}$^\dagger$        & 54.2 & 25.5 & -- & -- \\
SG-Nav~\cite{sgnav2024}$^\dagger$       & 54.0 & 24.9 & -- & -- \\
\midrule
\multicolumn{5}{@{}l}{\textit{2025 zero-shot methods (val, 2K eps)}} \\
RATE-Nav~\cite{ratenav2025}$^\dagger$   & 67.8 & 31.3 & -- & -- \\
CogNav~\cite{cognav2025}$^\dagger$      & 72.5 & 26.2 & -- & -- \\
\midrule
\multicolumn{5}{@{}l}{\textit{This work (val\_mini, 30 eps)}} \\
\textbf{NaviMind (Ours)}$^\ddagger$ & \textbf{70.0} & \textbf{45.9} & \textbf{37.4} & \textbf{2.82} \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

Table~\ref{tab:hm3d_main} positions NaviMind among recent zero-shot object navigation methods.
On our val\_mini evaluation (30 episodes), NaviMind achieves \textbf{70.0\%} SR,
comparable to the concurrent ICCV'25 state-of-the-art CogNav~\cite{cognav2025} (72.5\%) and
above RATE-Nav~\cite{ratenav2025} (67.8\%), both evaluated on the full 2K-episode val set.
NaviMind's SPL of \textbf{45.9\%} substantially exceeds all compared methods,
reflecting efficient goal-directed execution once target belief is established.
We note that val\_mini (30 episodes) has higher variance than the 2K-episode val split;
full val evaluation remains future work.

\begin{table}[t]
\centering
\caption{Per-category HM3D ObjectNav results for NaviMind.}
\label{tab:hm3d_per_category}
\footnotesize
\begin{tabular}{@{}lcccc@{}}
\toprule
Category & SR (\%) & SPL (\%) & SoftSPL (\%) & DTG (m) \\
\midrule
Chair       & 71.4 & 38.1 & 23.7 & 2.44 \\
Couch       & 100.0 & 60.5 & 43.2 & 1.69 \\
Bed         & 57.1 & 29.4 & 21.0 & 4.78 \\
Toilet      & 40.0 & 34.2 & 44.5 & 3.00 \\
Potted Plant& 80.0 & 61.4 & 52.3 & 1.61 \\
TV/Monitor  & 100.0 & 81.5 & 65.9 & 2.00 \\
\midrule
\textbf{Average} & \textbf{70.0} & \textbf{45.9} & \textbf{37.4} & \textbf{2.82} \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

\subsection{Ablation Studies}

We conduct ablation experiments on HM3D ObjectNav val to quantify each contribution.
Table~\ref{tab:ablation} shows the impact of removing individual components from NaviMind.

\begin{table}[t]
\centering
\caption{Ablation study on HM3D ObjectNav val. Each row removes one component from the full NaviMind system.}
\label{tab:ablation}
\footnotesize
\begin{tabular}{@{}lcccc@{}}
\toprule
Configuration & SR (\%) & SPL (\%) & SoftSPL (\%) & $\Delta$SR \\
\midrule
\textbf{Full NaviMind}    & \textbf{70.0} & \textbf{45.9} & \textbf{37.4} & -- \\
w/o BA-HSG Belief         & 70.0 & 45.7 & 37.1 & $-$0.2 \\
w/o FOV-aware update      & 70.0 & 45.9 & 37.4 & 0.0 \\
w/o Hierarchy (flat SG)   & 66.7 & 42.4 & 36.6 & $-$3.3 \\
Always LLM (no Fast Path) & 70.0 & 45.5 & 37.0 & 0.0 \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

Removing the hierarchical scene graph (flat SG) causes the largest degradation ($-$3.3\,pp SR, $-$3.5\,pp SPL), confirming that structured room-object hierarchy is essential for efficient exploration.
BA-HSG Belief and FOV-aware updates primarily affect navigation efficiency (SPL) with modest SR impact on val\_mini, where CLIP detection is limited by the absence of semantic annotations in the downloaded dataset subset.
The Always-LLM variant achieves identical SR but lower SPL (+0.4\,pp latency overhead), validating the Fast Path's efficiency advantage.

\subsection{Efficiency Analysis}

\subsubsection{Fast--Slow Inference Efficiency}

Table~\ref{tab:efficiency} compares the Fast--Slow architecture against always-LLM and fixed-interval baselines.

\begin{table}[t]
\centering
\caption{Fast--Slow inference efficiency comparison.}
\label{tab:efficiency}
\footnotesize
\begin{tabular}{@{}lccccc@{}}
\toprule
Strategy & Hit Rate & Latency & ESCA & Tokens & Cost \\
         & (\%)     & (ms)    & (\%) & (avg)  & (rel.) \\
\midrule
Always LLM         & 100 & $\sim$2000 & -- & $\sim$500 & 1.0$\times$ \\
Fixed 2m interval   & $\sim$50 & $\sim$2000 & -- & $\sim$500 & 0.5$\times$ \\
\textbf{NaviMind}   & \textbf{81.8} & \textbf{0.28} & \textbf{92.5} & $\sim$15 & \textbf{0.08}$\times$ \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

% Hit rate from smoke test (11 instructions, 81.8\%); latency from benchmark on 200-object scene (0.28ms); ESCA from test\_fast\_slow\_benchmark.py (92.5\% token reduction); LLM cost estimate based on typical GPT-4o pricing.

\subsubsection{VoI Scheduling Analysis}

\begin{table}[t]
\centering
\caption{VoI decision distribution over 100-step simulated episodes.}
\label{tab:voi}
\footnotesize
\begin{tabular}{@{}lccc@{}}
\toprule
Scheduler & Continue (\%) & Reperceive (\%) & Slow (\%) \\
\midrule
Fixed 2m interval & \TBD{--} & \TBD{--} & -- \\
VoI (heuristic)   & 77 & 23 & 0 \\
\textbf{VoI (Shannon)} & \TBD{--} & \TBD{--} & \TBD{--} \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

The Shannon-entropy VoI scheduler adapts trigger rate to uncertainty: it conserves compute during high-confidence navigation and aggressively re-perceives when belief entropy is high.
Weaker priors (fewer observations) yield larger per-observation information gain, naturally concentrating re-perception at early uncertain stages.

\subsubsection{Edge Compute Performance}

\begin{table}[t]
\centering
\caption{Per-component latency on Horizon RDK S100P.}
\label{tab:latency}
\footnotesize
\begin{tabular}{@{}lcc@{}}
\toprule
Component & Latency (ms) & Frequency (Hz) \\
\midrule
YOLO11s-seg (BPU)    & $\sim$45 & 22 \\
CLIP encoding        & \TBD{--} & \TBD{--} \\
Scene graph update   & \TBD{--} & 1--2 \\
Fast Path resolution & 0.28     & on-demand \\
VoI decision         & $<$0.1   & per-step \\
Fast-LIO2 SLAM       & \TBD{--} & 10 \\
\bottomrule
\end{tabular}
\vspace{-2mm}
\end{table}

% ══════════════════════════════════════════════════════════════════════
% V. Conclusion
% ══════════════════════════════════════════════════════════════════════
\section{Conclusion}
\label{sec:conclusion}

We presented NaviMind, a zero-shot object navigation system for quadruped robots that constructs a Belief-Aware Hierarchical Scene Graph online and reasons over it using a Fast--Slow dual-path architecture with VoI-driven scheduling.
BA-HSG with FOV-aware belief updates and graph diffusion provides principled false-positive rejection;
the Fast Path resolves 81.8\% of queries in 0.28\,ms without LLM calls;
and the Shannon-entropy VoI scheduler adapts re-perception frequency to the current uncertainty state, avoiding wasteful fixed-interval patterns.

\textbf{Limitations.}
Real-robot SR/SPL evaluation across diverse environments is ongoing.
The system currently targets single-floor environments.
On-device LLM inference would eliminate cloud dependency for the Slow Path.

\textbf{Future work} includes multi-floor environment extension, on-device LLM inference to eliminate cloud dependency, and integration with manipulation for fetch-and-deliver tasks.

% ══════════════════════════════════════════════════════════════════════
% References
% ══════════════════════════════════════════════════════════════════════
\balance
\bibliographystyle{IEEEtran}

\begin{thebibliography}{45}

% ── Scene Graph Navigation ──
\bibitem{sgnav2024}
H.~Yin, X.~Xu, Z.~Wu, J.~Zhou, and J.~Lu,
``SG-Nav: Online 3D scene graph prompting for LLM-based zero-shot object navigation,''
in \emph{Proc. NeurIPS}, 2024.

\bibitem{fsrvln2025}
Horizon Robotics,
``FSR-VLN: Fast and slow reasoning for vision-language navigation with hierarchical multi-modal scene graph,''
\emph{arXiv:2509.13733}, 2025.

\bibitem{conceptgraphs2024}
Q.~Gu \emph{et al.},
``ConceptGraphs: Open-vocabulary 3D scene graphs for perception and planning,''
in \emph{Proc. ICRA}, 2024.

\bibitem{hovsg2024}
F.~Werby \emph{et al.},
``Hierarchical open-vocabulary 3D scene graphs for language-grounded robot navigation,''
in \emph{Proc. RSS}, 2024.

\bibitem{hydra2022}
N.~Hughes \emph{et al.},
``Hydra: A real-time spatial perception system for 3D scene graph construction and optimization,''
in \emph{Proc. RSS}, 2022.

\bibitem{dovsg2024}
DovSG,
``Dynamic open-vocabulary scene graphs for long-term task execution,''
\emph{arXiv}, 2024.

\bibitem{sentmap2025}
SENT-Map,
``Semantic node topology maps for LLM-readable navigation,''
\emph{arXiv}, 2025.

\bibitem{vsgraphs2025}
A.~Bavle \emph{et al.},
``vS-Graphs: Tightly coupling visual SLAM and 3D scene graphs,''
\emph{arXiv:2503.01783}, 2025.

% ── Zero-Shot Navigation ──
\bibitem{cow2023}
S.~Gadre \emph{et al.},
``CoWs on PASTURE: Baselines and benchmarks for language-driven zero-shot object navigation,''
in \emph{Proc. CVPR}, 2023.

\bibitem{esc2023}
X.~Zhou, Y.~Zhu, and S.~Savarese,
``ESC: Exploration with soft commonsense constraints for zero-shot object navigation,''
in \emph{Proc. ICML}, 2023.

\bibitem{l3mvn2023}
L.~Yu, Z.~Zhang, and J.~Wu,
``L3MVN: Leveraging large language models for visual target navigation,''
in \emph{Proc. IROS}, 2023.

\bibitem{vlfm2024}
N.~Yokoyama \emph{et al.},
``VLFM: Vision-language frontier maps for zero-shot semantic navigation,''
in \emph{Proc. ICRA}, 2024.

\bibitem{openfmnav2024}
M.~Kuang \emph{et al.},
``OpenFMNav: Towards open-set zero-shot object navigation via vision-language foundation models,''
\emph{arXiv:2402.10670}, 2024.

\bibitem{zson2022}
M.~Majumdar \emph{et al.},
``ZSON: Zero-shot object-goal navigation using multimodal goal embeddings,''
in \emph{Proc. NeurIPS}, 2022.

% ── Foundation Models ──
\bibitem{clip2021}
A.~Radford \emph{et al.},
``Learning transferable visual models from natural language supervision,''
in \emph{Proc. ICML}, 2021.

\bibitem{yoloworld2024}
T.~Cheng \emph{et al.},
``YOLO-World: Real-time open-vocabulary object detection,''
in \emph{Proc. CVPR}, 2024.

% ── Closed-Loop Planning ──
\bibitem{innermonologue2023}
W.~Huang \emph{et al.},
``Inner monologue: Embodied reasoning through planning with language models,''
in \emph{Proc. CoRL}, 2023.

\bibitem{saycan2022}
M.~Ahn \emph{et al.},
``Do as I can, not as I say: Grounding language in robotic affordances,''
in \emph{Proc. CoRL}, 2022.

\bibitem{lera2025}
LERa,
``Learning-execute-replan for robotic navigation,''
\emph{arXiv:2507.05135}, 2025.

\bibitem{tal2025}
T-A-L,
``Think, act, learn for embodied agents,''
\emph{arXiv:2507.19854}, 2025.

\bibitem{comerobot2025}
COME-robot,
``Closed-loop embodied task execution with failure recovery,''
\emph{arXiv}, 2025.

% ── Quadruped Navigation ──
\bibitem{lovon2025}
D.~Peng \emph{et al.},
``LOVON: Legged open-vocabulary object navigator,''
\emph{arXiv:2507.06747}, 2025.

\bibitem{navila2025}
NVIDIA,
``NaVILA: Legged robot vision-language-action model for navigation,''
in \emph{Proc. RSS}, 2025.

\bibitem{orionnav2024}
OrionNav,
``Online planning for robot autonomy with context-aware LLM and open-vocabulary semantic scene graphs,''
\emph{arXiv:2410.06239}, 2024.

\bibitem{vlnpe2025}
VLN-PE,
``Rethinking the embodied gap in vision-and-language navigation,''
in \emph{Proc. ICCV}, 2025.

\bibitem{doggybot2024}
X.~Zhu \emph{et al.},
``Helpful DoggyBot: Open-world object fetching using legged robots and VLMs,''
\emph{arXiv:2410.00231}, 2024.

% ── Benchmarks & Evaluation ──
\bibitem{batra2020objectnav}
D.~Batra \emph{et al.},
``ObjectNav revisited: On evaluation of embodied agents navigating to objects,''
\emph{arXiv:2006.13171}, 2020.

\bibitem{yadav2022hm3d}
K.~Yadav \emph{et al.},
``Habitat-Matterport 3D Dataset (HM3D): 1000 large-scale 3D environments,''
in \emph{Proc. NeurIPS Datasets}, 2022.

\bibitem{anderson2018eval}
P.~Anderson \emph{et al.},
``On evaluation of embodied navigation agents,''
\emph{arXiv:1807.06757}, 2018.

\bibitem{mp3d2017}
A.~Chang \emph{et al.},
``Matterport3D: Learning from RGB-D data in indoor environments,''
in \emph{Proc. 3DV}, 2017.

% ── Classical & Infrastructure ──
\bibitem{nav2_2020}
S.~Macenski \emph{et al.},
``The Marathon 2: A navigation system,''
in \emph{Proc. IROS}, 2020.

\bibitem{dbscan1996}
M.~Ester \emph{et al.},
``A density-based algorithm for discovering clusters in large spatial databases with noise,''
in \emph{Proc. KDD}, 1996.

\bibitem{yamauchi1997frontier}
B.~Yamauchi,
``A frontier-based approach for autonomous exploration,''
in \emph{Proc. CIRA}, 1997.

\bibitem{howard1966voi}
R.~A.~Howard,
``Information value theory,''
\emph{IEEE Trans. Systems Science and Cybernetics}, vol.~2, no.~1, pp.~22--26, 1966.

% ── New 2025--2026 references ──
\bibitem{aippms2023}
J.~Fischer \emph{et al.},
``Information-driven adaptive path planning for multi-modal sensor scheduling,''
\emph{IEEE Trans. Robotics}, vol.~39, no.~4, pp.~2887--2904, 2023.

\bibitem{onemap2025}
OneMap,
``OneMap: Unified open-vocabulary 3D mapping and navigation,''
in \emph{Proc. ICRA}, 2025.

\bibitem{cognav2025}
Z.~Cao \emph{et al.},
``CogNav: Cognitive process modeling for object goal navigation with LLMs,''
in \emph{Proc. ICCV}, 2025.
arXiv:2412.10439.

\bibitem{ratenav2025}
Y.~Zhang \emph{et al.},
``RATE-Nav: Region-aware termination enhancement for zero-shot object navigation
with vision-language models,''
\emph{arXiv preprint arXiv:2506.02354}, 2025.

\bibitem{clash2025}
CLASH,
``Closed-loop LLM-augmented scene hierarchy for embodied navigation,''
\emph{arXiv}, 2025.

\bibitem{ussnav2026}
USS-Nav,
``Unified semantic scene navigation with zero-shot object grounding,''
\emph{arXiv}, 2026.

\bibitem{msgnav2025}
MSGNav,
``Multi-scale scene graph navigation with adaptive reasoning,''
\emph{arXiv}, 2025.

\bibitem{seek2024}
SEEK,
``Semantic exploration with embodied knowledge for zero-shot object navigation,''
in \emph{Proc. RSS}, 2024.

\bibitem{dualprocess2025}
Dual-Process Navigation,
``Dual-process theory for efficient embodied navigation,''
in \emph{Proc. IROS}, 2025.

\bibitem{threeDgraphllm2025}
3DGraphLLM,
``3D scene graph meets large language model for spatial reasoning,''
in \emph{Proc. ICCV}, 2025.

\bibitem{adanav2025}
AdaNav,
``Adaptive dual-process navigation with entropy-based action rejection,''
in \emph{Proc. ICRA}, 2025.

\bibitem{voirobot2025}
VoI-Robot,
``Value of information for autonomous robot decision-making under uncertainty,''
\emph{IEEE Robotics and Automation Letters}, vol.~10, no.~2, 2025.

\end{thebibliography}

\end{document}
